Active Learning for SAT Solver Benchmarking

### 2022-10-13 paper/paper.tex
Anonymize paper
Revert after review.

\author{
  Tobias Fuchs\orcidID{0000-0001-9727-2878} (\Letter) \and \\
  Jakob Bach\orcidID{0000-0003-0301-2798} \and \\
  Markus Iser\orcidID{0000-0003-2904-232X}
}

\institute{
  Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany \\
  \email{info@tobiasfuchs.de, jakob.bach@kit.edu, markus.iser@kit.edu}
}

\authorrunning{T. Fuchs et al.} % according to sample paper of template: first names are abbreviated; if there are more than two authors, 'et al.' is used.

@@

% TODO: insert URLs
All our source code\footnote{temporary, anonymized version for review: \url{xxx}} and and data\footnote{temporary, anonymized version for review: \url{xxx}} are available on GitHub.

@@

\begin{algorithm}
  \caption{Incremental Benchmarking Framework}
  \label{algALBenchmark}

@@

% TODO: insert URLs
For reproducibility, our source code and data are available on GitHub\footnote{temporary, anonymized version for review: \url{xxx}}.
Our code is implemented in \textsc{Python} using \emph{scikit-learn}~\cite{scikit-learn} for making predictions and \emph{gbd-tools}~\cite{IserS18} for SAT-instance retrieval.

>>>>

\author{
  Authors anonymized for review
  \vspace{0.4cm}
}

\institute{
  Institute anonymized for review
  \vspace{0.4cm}
}

\authorrunning{Authors anonymized for review} % according to sample paper of template: first names are abbreviated; if there are more than two authors, 'et al.' is used.

@@

All our source code\footnote{temporary reference, anonymized version for review: \url{https://github.com/dgnr7vexskfoc3a67jdtf96kd9opz/al-for-sat-solver-benchmarking}} and and data\footnote{temporary reference, anonymized version for review: \url{https://github.com/dgnr7vexskfoc3a67jdtf96kd9opz/al-for-sat-solver-benchmarking-data}} are available on GitHub.

@@

\begin{algorithm}[t]
  \caption{Incremental Benchmarking Framework}
  \label{algALBenchmark}

@@

For reproducibility, our source code and data are available on GitHub (cf. footnotes in Section~\ref{sec:intro}).
Our code is implemented in \textsc{Python} using \emph{scikit-learn}~\cite{scikit-learn} for making predictions and \emph{gbd-tools}~\cite{IserS18} for SAT-instance retrieval.
